%======================================================================
% REFERENCIAS BIBLIOGRÁFICAS
%======================================================================
\renewcommand{\bibname}{Referencias Bibliogr\'aficas}

\begin{thebibliography}{99}

\addcontentsline{toc}{chapter}{Referencias Bibliogr\'aficas}

\item Rep\'ublica Bolivariana de Venezuela. (2013). \textit{Ley de Infogobierno}. Gaceta Oficial N\~{u}m. 40.198.

\item Rep\'ublica Bolivariana de Venezuela. (2001). \textit{Ley Especial contra los Delitos Inform\'aticos}. Gaceta Oficial N\~{u}m 37.313.

\item Rep\'ublica Bolivariana de Venezuela. (2001). \textit{Ley sobre Mensajes de Datos y Firmas Electrónicas}. Gaceta Oficial N\~{u}m 37.518.

\item ISO/IEC. (2013). \textit{ISO/IEC 27001:2013 - Information security management systems}. International Organization for Standardization.

\item ISO. (2019). \textit{ISO 22301:2019 - Security and resilience - Business continuity management systems}.

\item NIST. (2020). \textit{SP 800-53 Rev. 5 - Security and Privacy Controls}. National Institute of Standards and Technology.

\item OWASP Foundation. (2021). \textit{OWASP Top 10 - Web Application Security Risks}.

\item Richards, M., \& Ford, N. (2020). \textit{Fundamentals of Software Architecture}. O'Reilly Media.

\item Newman, S. (2015). \textit{Building Microservices}. O'Reilly Media.

\item Kindred, J., \& Albeanu, G. (2022). \textit{Zero Trust Architecture}. IT Governance Publishing.

\item The Go Programming Language. (2024). \textit{The Go Programming Language Specification}. Google.

\item The Rust Team. (2024). \textit{The Rust Programming Language}. Rust Foundation.

\item Google. (2024). \textit{Angular Documentation}. Google.

\item Tauri Programme. (2024). \textit{Tauri Documentation}.

\item gRPC Authors. (2024). \textit{gRPC Documentation}. Google.

\item Dierks, T., \& Rescorla, E. (2018). \textit{RFC 8446 - TLS 1.3}. IETF.

\item Jones, M., Bradley, J., \& Sakimura, N. (2015). \textit{RFC 7519 - JSON Web Token (JWT)}. IETF.

\item Jon G. (2023). \textit{Rust for Rustaceans}. No Starch Press.

\item Meyers, B. (2023). \textit{Effective TypeScript}. O'Reilly Media.

\item Ministerio del Poder Popular para la Educaci\'on. (2020). \textit{Plan Nacional de Soberan\'{\i}a Tecnol\'ogica}. Rep\'ublica Bolivariana de Venezuela.

\end{thebibliography}

\newpage
